High-Performance Data Analysis on Janus using Apache Spark

### 2013-12-16 paper.tex
added outline to eval, results, and discussion sections

>>>>

\section{Introduction}

\section{Overview}

\section{Evaluation}
% janus
    % overview
%%% DIRECTLY COPY-PASTED TEXT %%%
University of the University of Colorado's Top-
31 (June 2010) supercomputer system, Janus
    % specs (ref)
%%% DIRECTLY COPY-PASTED TEXT %%%
The final Janus computational
system consists of 1,368 nodes, each containing two six-
core Intel Xeon Westmere-EP chips at 2.8 GHz, for a total
of 2,736 processors and 16,416 cores with a theoretical
peak performance of 184 TFLOP/s. Each core has 2
GB of 1333 MHz DDR3 RAM for a total of 24 GB per
node and 32 TB of memory in the entire system. [REF]
% spark
    % reason for spark (diskless)
    % installation (default???)
    % version number (Spark 0.8.0, Scala 2.9.3)
% purpose of trials (speedup, efficiency, install on Janus)
    % find ideal configurations

\subsection{Testing}
% grep
    % overview
    % program source
    % grep complexity
    % file content
    % files sizes
    % node core counts
    % serial runtime
    % workers per node
% page rank
    % overview
    % ...

\subsection{Results}
% small grep test
    % serial run time (graph)
    % efficiency (graph)
    % karp flatt (graph)
% cores grep test
    % scale up, workers per node (graph)
% large grep test
    % serial run time (graph)
    % efficiency (graph)
% pagerank test 1
% pagerank test 2
% ...

\section{Discussion}
% small grep test
    % ideal balance between speedup and efficiency
% cores grep test
    % ideal number of workers per core
    % close enough not to matter
    % don't use 6-12
% large grep test
    % ideal workers per problem size
    % follow up test with delay
    % delay (graph)
    % take away on IO
% pagerank test 1
% pagerank test 2
% ...

% workings and master comm of spark protocol

\section{Conclusion}
